R Notebook

### 2019-10-15 src/plots for paper.Rmd
update to depth plot + land trim... now working on reversing cols

pm <- ggplot(mar, aes(Depth, p_cells, fill = Probability)) + geom_col() + coord_flip() + scale_fill_viridis(option="viridis", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsm, breaks=flevelsm[seq(1,length(flevelsm), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "March") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pj <- ggplot(jun, aes(Depth, p_cells, fill = Probability)) + geom_col() + coord_flip() +  scale_fill_manual(values = probcol) + scale_x_discrete(limits = flevelsj, breaks=flevelsj[seq(1,length(flevelsj), by = 2)]) + coord_flip() +labs(y = "% Ocean at Depth", title = "June") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

ps <- ggplot(sep, aes(Depth, p_cells, fill = Probability)) + geom_col() + coord_flip() +  scale_fill_manual(values = probcol) + scale_x_discrete(limits = flevelss, breaks=flevelss[seq(1,length(flevelss), by = 2)]) + coord_flip() +labs(y = "% Ocean at Depth", title = "September") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pd <- ggplot(dec, aes(Depth, p_cells, fill = Probability)) + geom_col() + coord_flip() +  scale_fill_manual(values = probcol) + scale_x_discrete(limits = flevelsd, breaks=flevelsd[seq(1,length(flevelsd), by = 2)]) + coord_flip() +labs(y = "% Ocean at Depth", title = "December") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

>>>>

pm <- ggplot(mar, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="viridis", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsm, breaks=flevelsm[seq(1,length(flevelsm), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "March") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pj <- ggplot(jun, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() +  scale_fill_manual(values = probcol) + scale_x_discrete(limits = flevelsj, breaks=flevelsj[seq(1,length(flevelsj), by = 2)]) + coord_flip() +labs(y = "% Ocean at Depth", title = "June") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

ps <- ggplot(sep, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() +  scale_fill_manual(values = probcol) + scale_x_discrete(limits = flevelss, breaks=flevelss[seq(1,length(flevelss), by = 2)]) + coord_flip() +labs(y = "% Ocean at Depth", title = "September") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pd <- ggplot(dec, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() +  scale_fill_manual(values = probcol) + scale_x_discrete(limits = flevelsd, breaks=flevelsd[seq(1,length(flevelsd), by = 2)]) + coord_flip() +labs(y = "% Ocean at Depth", title = "December") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

### 2019-10-15 src/testing_file.Rmd
update to depth plot + land trim... now working on reversing cols

the maps need to be layered with the land etc, trimmed, and coloured to whatever is agreed

```{r}
aea <- raster("../output/env/aea.tif") #the correct CRS
maplst <- list.files("../output/maxent/paper_plots/hotspot_mapping/", pattern = "_bin_0.5_2d.*.asc", full.names = TRUE)
s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
apr <- aea@crs
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis

cumasc <- raster(maplst[1])
cumasc2 <- raster(maplst[2])
cumasc <- raster::mask(cumasc, outsidemcp, inverse = TRUE)
cumasc2 <- raster::mask(cumasc2, outsidemcp, inverse = TRUE)
ss <- raster::mask(s, outsidemcp, inverse = TRUE) #HERE NEED TO WORK OUT HOW TO CLIP LAND

@@

my.at <- seq(0, 1, by = 0.1)
mapTheme <- viridisTheme(region = viridis(10))

p <- levelplot(pstack, ylab = NULL, xlab = NULL, scales=list(draw=FALSE), colorkey=list(space="bottom", at = my.at), par.settings = mapTheme, layout = c(2, 1), names.attr = c("6m", "180m"), margin = FALSE)
p + layer(sp.polygons(s, fill = "black")) 
cumasc <- raster::mask(p, outsidemcp, inverse = TRUE)

>>>>

#trimming maps to mcp

```{r}
library(viridis)
library(rasterVis)

aea <- raster("../output/env/aea.tif") #the correct CRS
maplst <- list.files("../output/maxent/paper_plots/hotspot_mapping/", pattern = "_bin_0.5_2d.*.asc", full.names = TRUE)
s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
apr <- aea@crs
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis
mcp <- shapefile("../output/bio/minimum_convex_poly/mcp_capelin_100_poly.shp")

cumasc <- raster(maplst[1])
cumasc2 <- raster(maplst[2])
cumasc <- raster::mask(cumasc, mcp)
cumasc2 <- raster::mask(cumasc2, mcp)
ss <- raster::intersect(s, mcp)

@@

my.at <- seq(0, 1, by = 0.1)
mapTheme <- viridisTheme(region = viridis(10), direction = -1)

p <- levelplot(pstack, ylab = NULL, xlab = NULL, scales=list(draw=FALSE), colorkey=list(space="bottom", at = my.at), par.settings = mapTheme, layout = c(2, 1), names.attr = c("6m", "180m"), margin = FALSE) + layer(sp.polygons(ss, fill = "red")) 
plot(p)

pm <- ggplot(mar, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="viridis", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsm, breaks=flevelsm[seq(1,length(flevelsm), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "March") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))
